A decade of biodiversity change in an estuarine assemblage: fits and starts and natural events

### 2022-09-28 sub-projects/trawl/docs/ms/ms.RMD
updated ms

Anthropogenic activities continue to exert long-term, varied, and increasing pressures on marine ecosystems causing alterations to biological diversity on broad and local scales. Shifts in biodiversity are variable, nuanced and difficult to predict, yet, understanding how communities change through time is crucial for predicting current and future changes to biological systems and the services they provide. We document a decade of biodiversity change in a shallow estuarine nekton community...

@@

### create timeseries figure
mth_group_stats %>%
  dplyr::filter(index == 'S_n') %>%
  ggplot(aes( x= Date, y = median))+
  scale_y_continuous(name = expression("Rarefied richness ("~italic(~S[n])~")"), limits = c(1,12),
                     breaks = c(1,5,10),expand = c(0.01,0.01))+
  scale_x_date(date_breaks = "year", limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
               date_labels = "%Y",expand = c(0.01,0.01))+
  geom_point(size = 2)+
  geom_line(size = 1.2)+
  theme_tufte()+
  geom_rangeframe(sides = "l")+
  annotate('text', label = "A", x = as.Date("2009-01-30"), y = 11, family ='serif', size = 8, hjust = 0)+
  theme(axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        # panel.grid.minor.x = element_line(color = 'lightgray'),
        plot.margin = unit(c(0.0,0.1,-0.1,0.0), 'cm'), 
        plot.background = element_rect(fill = 'transparent', color = NA),
        panel.background = element_rect(fill = 'transparent', color = NA),
        axis.title.y = element_text(family = 'serif', size = 16),
        axis.text = element_text(family = 'serif', size = 14)) -> rich_time;

trawl_mth_turnover %>%
  dplyr::filter(variable == 'total') %>%
  na.omit %>%
  ggplot(aes(x = Date, y = value, group = variable, color = variable))+
  geom_point(size = 2)+
  geom_line(size = 1.2)+
  scale_color_manual(values = viridis(n = 1, option = 'viridis', begin = .75))+
  scale_y_continuous(name = 'Species turnover',limits = c(0,1), expand = c(0.01,0.01),
                     breaks = c(0,0.2 ,0.4, 0.6, 0.8), labels = c(0,0.2,0.4,0.6,0.8))+
  scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
               date_labels = "%Y",expand = c(0.01,0.01))+
  theme_tufte()+
  geom_rangeframe(sides = "lb", color = 'black')+
  annotate('text', label = "B", x = as.Date("2009-01-30"), y = 1, family = 'serif', vjust = 1, size = 8, hjust = 0)+
  theme(legend.position = "none",
        legend.justification = c(0,1),
        axis.title.x = element_blank(),
        plot.margin = unit(c(-0.18,0.15,0.0,0.0), 'cm'),
        # panel.grid.minor.x = element_line(color = 'lightgray'),
        plot.background = element_rect(fill = 'transparent', color = NA), 
        axis.title.y = element_text(family = 'serif', size = 16),
        axis.text = element_text(family = 'serif', size = 14)) -> turnover_time

@@

hill_time_df %>%
  dplyr::select(Date, date_id, q0.1_eff, q0.5_eff, q2_eff) %>%
  pivot_longer(-Date:-date_id, names_to = "qD", values_to = "value") %>%
  bind_rows(ceff_full) %>%
  ggplot(aes(x = Date, y = value, group = qD, color = qD))+
  geom_ribbon(data = na.omit(ceff_full), aes(x = Date, ymin = lower, ymax = upper, group = qD, fill = qD),
              color = NA, alpha =0.3, inherit.aes = FALSE)+
  geom_line(data= na.omit(ceff_full), aes(x = Date, y = estimate, group = qD, color = qD), inherit.aes = FALSE)+
  geom_point(size = 1.5,show.legend=FALSE)+
  geom_path(size = 1.2,show.legend=FALSE)+
  guides(fill = 'none')+
  theme_tufte()+
  geom_rangeframe(data = hill_time_df %>%
  dplyr::select(Date, date_id, q0.1_eff, q0.5_eff, q2_eff) %>%
  pivot_longer(-Date:-date_id, names_to = "qD", values_to = "value"), aes(x = Date, y =value), sides = "bl", color = 'black', inherit.aes = FALSE)+
  scale_color_manual(values = viridis(n = 3),labels = c(expression(italic(''^0.1*D)),
                                                        expression(italic(''^1*D)),
                                                        expression(italic(''^2*D)))) +
  scale_fill_manual(values = viridis(n = 3),labels = c(expression(italic(''^0.1*D)),
                                                       expression(italic(''^1*D)),
                                                       expression(italic(''^2*D))))+
  scale_y_continuous(name = expression("Effective species (%)"), limits = c(0,100),
                     expand = c(0.01,0.01)) +
  scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
               date_labels = "%Y", expand = c(0.01,0.01))+
  guides(color = guide_legend(nrow = 1))+
  annotate('text', label = 'A', x = as.Date("2009-01-01"), y = Inf, size = 8, hjust = 0, vjust = 1, family ='serif')+
  theme(axis.title.x = element_blank(),
        legend.title = element_blank(),
        legend.background = element_rect(fill = 'transparent', color = NA),
        legend.position = c(0,0),
        legend.justification = c(0,0)) -> hill_time_plot

@@

qD_coefs_df %>% 
  ungroup %>%
  dplyr::filter(q != 0) %>%
  ggplot()+
  geom_ribbon(aes(y = q, xmin = Q2.5, xmax = Q97.5), color = 'lightgrey', alpha = 0.3)+
  geom_ribbon(aes(y = q, xmin = Q25, xmax = Q75), color = 'lightgrey', alpha = 0.5)+
  geom_path(aes(y = q, x = Estimate), size = 1.2)+
  annotate('text', label = 'B', x = -2.5, y = 0, hjust = 0, vjust = 1, size = 8, family = 'serif')+
  theme_tufte()+
  geom_rangeframe(data = qD_coefs_df %>% 
  ungroup %>%
  dplyr::filter(q != 0),
  sides = "br", color = "black")+
  scale_y_continuous(name = expression(italic(""^q*"D")), 
                         trans = scales::reverse_trans(),
                     limits = c(3,0), expand = c(0.01,0.01), position = 'right')+
  scale_x_continuous(name = expression('Temporal trend ('*Delta*'%/year)'),
                     expand = c(0.01,0.01), limits = c(-2.5,0)) -> qD_trend_plot

@@

```{r spp contributions, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Figure 5."}

@@

## Make plots
q0.1_dis_plot = TB_trawl_q0.1_dis %>%
  dplyr::mutate(Common_name = factor(Common_name, levels = make.names(TB_trawl_order)),
                common_label = factor(common_label, levels = TB_trawl_order_names[make.names(TB_trawl_order)])) %>%
  slice_head(n = 20) %>%
  ggplot()+
  geom_col(aes(x= common_label, y = value))+
  scale_y_continuous(name = "Species contribution", limits = c(0,0.06), expand = c(0.0001,0.0001))+
  theme_tufte()+
  geom_rangeframe(sides = "bl", color = "black")+
  annotate("text", label = expression(italic(""^q*"D = 0.1")), x = Inf, y = Inf, vjust = 1, hjust = 1, size = 8, family = "serif")+
  theme(axis.text.x = element_blank(),
        axis.title = element_blank());

q0.5_dis_plot = TB_trawl_q0.5_dis %>%
  dplyr::mutate(Common_name = factor(Common_name, levels = make.names(TB_trawl_order)),
                common_label = factor(common_label, levels = TB_trawl_order_names[make.names(TB_trawl_order)])) %>%
    slice_head(n = 20) %>%
ggplot()+
  geom_col(aes(x= common_label, y = value))+
  scale_y_continuous(name = "Species contribution", limits = c(0,NA), expand = c(0.0001,0.0001))+
  theme_tufte()+
  geom_rangeframe(sides = "bl", color = "black")+
  annotate("text", label = expression(italic(""^q*"D = 0.5")), x = Inf, y = Inf, vjust = 1, hjust = 1, size = 8, family = "serif")+
  theme(axis.text.x = element_blank(),
        axis.title = element_blank());

q1_dis_plot = TB_trawl_q1_dis %>%
  dplyr::mutate(Common_name = factor(Common_name, levels = make.names(TB_trawl_order)),
                common_label = factor(common_label, levels = TB_trawl_order_names[make.names(TB_trawl_order)])) %>%
    slice_head(n = 20) %>%
ggplot()+
  geom_col(aes(x= common_label, y = value))+
  scale_y_continuous(name = "Species contribution", limits = c(0,NA), expand = c(0.0001,0.0001))+
  theme_tufte()+
  geom_rangeframe(sides = "bl", color = "black")+
  annotate("text", label = expression(italic(""^q*"D = 1")), x = Inf, y = Inf, vjust = 1, hjust = 1, size = 8, family = "serif")+
  theme(axis.text.x = element_blank(),
        axis.title = element_blank());

q2_dis_plot = TB_trawl_q2_dis %>%
  dplyr::mutate(Common_name = factor(Common_name, levels = make.names(TB_trawl_order)),
                common_label = factor(common_label, levels = TB_trawl_order_names[make.names(TB_trawl_order)])) %>%
    slice_head(n = 20) %>%
ggplot()+
  geom_col(aes(x= common_label, y = value))+
  scale_y_continuous(name = "Species contribution", limits = c(0,NA), expand = c(0.0001,0.0001))+
  theme_tufte()+
  geom_rangeframe(sides = "bl", color = "black")+
  annotate("text", label = expression(italic(""^q*"D = 2")), x = Inf, y = Inf, vjust = 1, hjust = 1, size = 8, family = "serif")+
  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust = 1),
        axis.title = element_blank())

@@

TB_q2_spp_plot = TB_q2_spp_df %>%
  ggplot()+
  geom_line(aes(x = Date, y = scale_n, group = Common_name, color = Common_name), size = 1.2)+
  scale_color_viridis(discrete = TRUE)+
  scale_y_continuous(name = "Scaled Abundance", expand = c(0.01,0.01))+
  scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
               date_labels = "%Y", expand = c(0.01,0.01))+
  theme_tufte()+
  geom_rangeframe(data = TB_q2_spp_df, aes(x = Date, y = scale_n),
                  sides = 'bl', color = 'black', inherit.aes = FALSE)+
  annotate('text', label = expression(italic(""^q*"D = 2")), x = as.Date("2019-12-31"), y = Inf, vjust = 1, hjust = 1, size = 8, family = 'serif')+
  theme(legend.title = element_blank(),
        axis.title.x = element_blank(),
        legend.position = c(0,1),
        legend.justification = c(0,1),
        legend.background = element_rect(fill = 'transparent', color = NA));TB_q2_spp_plot

TB_q1_spp_plot = TB_q1_spp_df %>%
  ggplot()+
  geom_line(aes(x = Date, y = scale_n, group = Common_name, color = Common_name), size = 1.2)+
  scale_color_viridis(discrete = TRUE)+
  scale_y_continuous(name = "Scaled Abundance", expand = c(0.01,0.01))+
  scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
               date_labels = "%Y", expand = c(0.01,0.01))+
  theme_tufte()+
  geom_rangeframe(data = TB_q1_spp_df, aes(x = Date, y = scale_n),
                  sides = 'bl', color = 'black', inherit.aes = FALSE)+
  annotate('text', label = expression(italic(""^q*"D = 1")), x = as.Date("2019-12-31"), y = Inf, vjust = 1, hjust = 1, size = 8, family = 'serif')+
  theme(legend.title = element_blank(),
        axis.title.x = element_blank(),
        legend.position = c(0,1),
        legend.justification = c(0,1),
        legend.background = element_rect(fill = 'transparent', color = NA));TB_q1_spp_plot

TB_q0.5_spp_plot = TB_q0.5_spp_df %>%
  ggplot()+
  geom_line(aes(x = Date, y = scale_n, group = Common_name, color = Common_name), size = 1.2)+
  scale_color_viridis(discrete = TRUE)+
  scale_y_continuous(name = "Scaled Abundance", expand = c(0.01,0.01))+
  scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
               date_labels = "%Y", expand = c(0.01,0.01))+
  theme_tufte()+
  geom_rangeframe(data = TB_q0.5_spp_df, aes(x = Date, y = scale_n),
                  sides = 'bl', color = 'black', inherit.aes = FALSE)+
  annotate('text', label = expression(italic(""^q*"D = 0.5")), x = as.Date("2019-12-31"), y = Inf, vjust = 1, hjust = 1, size = 8, family = 'serif')+
  theme(legend.title = element_blank(),
        axis.title.x = element_blank(),
        legend.position = c(0,1),
        legend.justification = c(0,1),
        legend.background = element_rect(fill = 'transparent', color = NA));TB_q0.5_spp_plot

TB_q0.1_spp_plot = TB_q0.1_spp_df %>%
  ggplot()+
  geom_line(aes(x = Date, y = scale_n, group = Common_name, color = Common_name))+
  scale_color_viridis(discrete = TRUE)+
  scale_y_continuous(name = "Scaled Abundance", expand = c(0.01,0.01))+
  scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
               date_labels = "%Y", expand = c(0.01,0.01))+
  theme_tufte()+
  geom_rangeframe(data = TB_q0.1_spp_df, aes(x = Date, y = scale_n),
                  sides = 'bl', color = 'black', inherit.aes = FALSE)+
  annotate('text', label = expression(italic(""^q*"D = 0.1")), x = as.Date("2019-12-31"), y = Inf, vjust = 1, hjust = 1, size = 8, family = 'serif')+
  theme(legend.title = element_blank(),
        axis.title.x = element_blank(),
        legend.position = c(0,1),
        legend.justification = c(0,1),
        legend.background = element_rect(fill = 'transparent', color = NA));TB_q0.1_spp_plot

grid.draw(rbind(ggplotGrob(TB_q1_spp_plot), ggplotGrob(TB_q2_spp_plot), size = 'last'))

@@

```{r trawl contributions,echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Figure 6. The contribution of individual trawl-dates to dissimilarity of the entire timeseries for diversity order q = 0.1 (top), q = 1 (middle), and q = 2 (bottom)." }

@@

TB_trawl_q2_dis2 = dis1(TB_trawl_taxasite_dis, q = 2, type = 'tax', type2 = 'k') %>%
  data.frame(check.names = FALSE) %>% 
  rownames_to_column('dis_type') %>%
  pivot_longer(-dis_type,names_to ='date_id', values_to = 'value') %>%
  dplyr::mutate(date_id = as.numeric(date_id)) %>%
  left_join(TB_trawl_taxasite %>% dplyr::select(Date, date_id))
TB_trawl_q0_dis2 = dis1(TB_trawl_taxasite_dis, q = 0, type = 'tax', type2 = 'k') %>%
  data.frame(check.names = FALSE) %>% 
  rownames_to_column('dis_type') %>%
  pivot_longer(-dis_type,names_to ='date_id', values_to = 'value') %>%
  dplyr::mutate(date_id = as.numeric(date_id)) %>%
  left_join(TB_trawl_taxasite %>% dplyr::select(Date, date_id))

@@

# plot contributions of each trawl to differences
TB_trawl_q0_dis2 %>%
  dplyr::filter(dis_type == "UqN")%>%
  ggplot(aes(x = Date, y = value))+
  geom_point()+
  geom_path()+
  scale_y_continuous(expand = c(0.0001,0.0001))+
   scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
               date_labels = "%Y")+
  theme(axis.title = element_blank(),
        axis.text.x = element_blank())-> TB_q0_dis2_plot

TB_trawl_q0.1_dis2 %>%
  dplyr::filter(dis_type == "UqN")%>%
  ggplot(aes(x = Date, y = value))+
  geom_point()+
  geom_path()+
  scale_y_continuous(expand = c(0.0001,0.0001))+
   scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
               date_labels = "%Y")+
  theme(axis.title = element_blank(),
        axis.text.x = element_blank())-> TB_q0.1_dis2_plot

TB_trawl_q1_dis2 %>%
  dplyr::filter(dis_type == "UqN")%>%
  ggplot(aes(x = Date, y = value))+
  geom_point()+
  geom_path()+
  scale_y_continuous(expand = c(0.0001,0.0001))+
   scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
               date_labels = "%Y")+
  theme(axis.title = element_blank(),
        axis.text.x = element_blank())-> TB_q1_dis2_plot
TB_trawl_q2_dis2 %>%
  dplyr::filter(dis_type == "UqN")%>%
  ggplot(aes(x = Date, y = value))+
  geom_point()+
  geom_path()+
  annotate('text', label = "")+
  scale_y_continuous(expand = c(0.0001,0.0001))+
   scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
               date_labels = "%Y")+
  theme(axis.title= element_blank()) -> TB_q2_dis2_plot

grid.draw(rbind(ggplotGrob(TB_q0.1_dis2_plot),
                ggplotGrob(TB_q1_dis2_plot), 
                ggplotGrob(TB_q2_dis2_plot), size = 'last'))
```

>>>>

Anthropogenic activities continue to exert long-term, varied, and increasing pressures on marine ecosystems causing alterations to biological diversity on broad and local scales. Shifts in biodiversity are variable, nuanced and difficult to predict, yet, understanding how communities change through time is crucial for predicting current and future changes to biological systems and the services they provide. We document a decade of biodiversity change in the nekton community of a shallow-estuary...

@@

### create timeseries figure
mth_group_stats %>%
  dplyr::filter(index == 'S_n') %>%
  ggplot(aes( x= Date, y = median))+
  scale_y_continuous(name = expression("Rarefied richness ("~italic(~S[n])~")"), limits = c(1,12),
                     breaks = c(1,5,10),expand = c(0.01,0.01))+
  scale_x_date(date_breaks = "year", limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
               date_labels = "%Y",expand = c(0.01,0.01))+
  geom_point(size = 2)+
  geom_line(size = 1.2)+
  theme_tufte()+
  geom_rangeframe(sides = "l")+
  annotate('text', label = "A", x = as.Date("2009-01-30"), y = 11, family ='serif', size = 6, hjust = 0)+
  theme(axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        # panel.grid.minor.x = element_line(color = 'lightgray'),
        plot.margin = unit(c(0.0,0.1,-0.1,0.0), 'cm'), 
        plot.background = element_rect(fill = 'transparent', color = NA),
        panel.background = element_rect(fill = 'transparent', color = NA),
        axis.title.y = element_text(family = 'serif', size = 16),
        axis.text = element_text(family = 'serif', size = 14)) -> rich_time;

trawl_mth_turnover %>%
  dplyr::filter(variable == 'total') %>%
  na.omit %>%
  ggplot(aes(x = Date, y = value, group = variable, color = variable))+
  geom_point(size = 2)+
  geom_line(size = 1.2)+
  scale_color_manual(values = viridis(n = 1, option = 'viridis', begin = .75))+
  scale_y_continuous(name = 'Species turnover',limits = c(0,1), expand = c(0.01,0.01),
                     breaks = c(0,0.2 ,0.4, 0.6, 0.8), labels = c(0,0.2,0.4,0.6,0.8))+
  scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
               date_labels = "%Y",expand = c(0.01,0.01))+
  theme_tufte()+
  geom_rangeframe(sides = "lb", color = 'black')+
  annotate('text', label = "B", x = as.Date("2009-01-30"), y = 1, family = 'serif', vjust = 1, size = 6, hjust = 0)+
  theme(legend.position = "none",
        legend.justification = c(0,1),
        axis.title.x = element_blank(),
        plot.margin = unit(c(-0.18,0.15,0.0,0.0), 'cm'),
        # panel.grid.minor.x = element_line(color = 'lightgray'),
        plot.background = element_rect(fill = 'transparent', color = NA), 
        axis.title.y = element_text(family = 'serif', size = 16),
        axis.text = element_text(family = 'serif', size = 14)) -> turnover_time

@@

hill_time_df %>%
  dplyr::select(Date, date_id, q0.1_eff, q0.5_eff, q2_eff) %>%
  pivot_longer(-Date:-date_id, names_to = "qD", values_to = "value") %>%
  bind_rows(ceff_full) %>%
  ggplot(aes(x = Date, y = value, group = qD, color = qD))+
  geom_ribbon(data = na.omit(ceff_full), aes(x = Date, ymin = lower, ymax = upper, group = qD, fill = qD),
              color = NA, alpha =0.3, inherit.aes = FALSE)+
  geom_line(data= na.omit(ceff_full), aes(x = Date, y = estimate, group = qD, color = qD), inherit.aes = FALSE)+
  geom_point(size = 1.5,show.legend=FALSE)+
  geom_path(size = 1.2,show.legend=FALSE)+
  guides(fill = 'none')+
  theme_tufte()+
  geom_rangeframe(data = hill_time_df %>%
  dplyr::select(Date, date_id, q0.1_eff, q0.5_eff, q2_eff) %>%
  pivot_longer(-Date:-date_id, names_to = "qD", values_to = "value"), aes(x = Date, y =value), sides = "bl", color = 'black', inherit.aes = FALSE)+
  scale_color_manual(values = viridis(n = 3),labels = c(expression(italic(''^0.1*D)),
                                                        expression(italic(''^1*D)),
                                                        expression(italic(''^2*D)))) +
  scale_fill_manual(values = viridis(n = 3),labels = c(expression(italic(''^0.1*D)),
                                                       expression(italic(''^1*D)),
                                                       expression(italic(''^2*D))))+
  scale_y_continuous(name = expression("Effective species (%)"), limits = c(0,100),
                     expand = c(0.01,0.01)) +
  scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
               date_labels = "%Y", expand = c(0.01,0.01))+
  guides(color = guide_legend(nrow = 1))+
  annotate('text', label = 'A', x = as.Date("2009-01-01"), y = Inf, size = 6, hjust = 0, vjust = 1, family ='serif')+
  theme(axis.title.x = element_blank(),
        legend.title = element_blank(),
        legend.background = element_rect(fill = 'transparent', color = NA),
        legend.position = c(0,0),
        legend.justification = c(0,0)) -> hill_time_plot

@@

qD_coefs_df %>% 
  ungroup %>%
  dplyr::filter(q != 0) %>%
  ggplot()+
  geom_ribbon(aes(y = q, xmin = Q2.5, xmax = Q97.5), color = 'lightgrey', alpha = 0.3)+
  geom_ribbon(aes(y = q, xmin = Q25, xmax = Q75), color = 'lightgrey', alpha = 0.5)+
  geom_path(aes(y = q, x = Estimate), size = 1.2)+
  annotate('text', label = 'B', x = -2.5, y = 0, hjust = 0, vjust = 1, size = 6, family = 'serif')+
  theme_tufte()+
  geom_rangeframe(data = qD_coefs_df %>% 
  ungroup %>%
  dplyr::filter(q != 0),
  sides = "br", color = "black")+
  scale_y_continuous(name = expression(italic(""^q*"D")), 
                         trans = scales::reverse_trans(),
                     limits = c(3,0), expand = c(0.01,0.01), position = 'right')+
  scale_x_continuous(name = expression('Temporal trend ('*Delta*'%/year)'),
                     expand = c(0.01,0.01), limits = c(-2.5,0)) -> qD_trend_plot

@@

```{r spp contributions, fig.height=8, fig.width=3.5, dpi=450, fig.cap="Figure 5."}

@@

## Make plots
q0.1_dis_plot = TB_trawl_q0.1_dis %>%
  dplyr::mutate(Common_name = factor(Common_name, levels = make.names(TB_trawl_order)),
                common_label = factor(common_label, levels = TB_trawl_order_names[make.names(TB_trawl_order)])) %>%
  slice_head(n = 20) %>%
  ggplot()+
  geom_col(aes(x= common_label, y = value))+
  scale_y_continuous(name = "Species contribution", limits = c(0,0.06), expand = c(0.0001,0.0001))+
  theme_tufte()+
  geom_rangeframe(sides = "bl", color = "black")+
  annotate("text", label = expression(italic(""^q*"D = 0.1")), x = Inf, y = Inf, vjust = 1, hjust = 1, size = 6, family = "serif")+
  theme(axis.text.x = element_blank(),
        axis.title = element_blank());

q0.5_dis_plot = TB_trawl_q0.5_dis %>%
  dplyr::mutate(Common_name = factor(Common_name, levels = make.names(TB_trawl_order)),
                common_label = factor(common_label, levels = TB_trawl_order_names[make.names(TB_trawl_order)])) %>%
    slice_head(n = 20) %>%
ggplot()+
  geom_col(aes(x= common_label, y = value))+
  scale_y_continuous(name = "Species contribution", limits = c(0,NA), expand = c(0.0001,0.0001))+
  theme_tufte()+
  geom_rangeframe(sides = "bl", color = "black")+
  annotate("text", label = expression(italic(""^q*"D = 0.5")), x = Inf, y = Inf, vjust = 1, hjust = 1, size = 6, family = "serif")+
  theme(axis.text.x = element_blank(),
        axis.title = element_blank());

q1_dis_plot = TB_trawl_q1_dis %>%
  dplyr::mutate(Common_name = factor(Common_name, levels = make.names(TB_trawl_order)),
                common_label = factor(common_label, levels = TB_trawl_order_names[make.names(TB_trawl_order)])) %>%
    slice_head(n = 20) %>%
ggplot()+
  geom_col(aes(x= common_label, y = value))+
  scale_y_continuous(name = "Species contribution", limits = c(0,NA), expand = c(0.0001,0.0001))+
  theme_tufte()+
  geom_rangeframe(sides = "bl", color = "black")+
  annotate("text", label = expression(italic(""^q*"D = 1")), x = Inf, y = Inf, vjust = 1, hjust = 1, size = 6, family = "serif")+
  theme(axis.text.x = element_blank(),
        axis.title = element_blank());

q2_dis_plot = TB_trawl_q2_dis %>%
  dplyr::mutate(Common_name = factor(Common_name, levels = make.names(TB_trawl_order)),
                common_label = factor(common_label, levels = TB_trawl_order_names[make.names(TB_trawl_order)])) %>%
    slice_head(n = 20) %>%
ggplot()+
  geom_col(aes(x= common_label, y = value))+
  scale_y_continuous(name = "Species contribution", limits = c(0,NA), expand = c(0.0001,0.0001))+
  theme_tufte()+
  geom_rangeframe(sides = "bl", color = "black")+
  annotate("text", label = expression(italic(""^q*"D = 2")), x = Inf, y = Inf, vjust = 1, hjust = 1, size = 6, family = "serif")+
  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust = 1),
        axis.title = element_blank())

@@

TB_q2_spp_plot = TB_q2_spp_df %>%
  ggplot()+
  geom_line(aes(x = Date, y = scale_n, group = Common_name, color = Common_name), size = 1.2)+
  scale_color_viridis(discrete = TRUE)+
  scale_y_continuous(name = "Scaled Abundance", expand = c(0.01,0.01))+
  scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
               date_labels = "%Y", expand = c(0.01,0.01))+
  theme_tufte()+
  geom_rangeframe(data = TB_q2_spp_df, aes(x = Date, y = scale_n),
                  sides = 'bl', color = 'black', inherit.aes = FALSE)+
  annotate('text', label = expression(italic(""^q*"D = 2")), x = as.Date("2019-12-31"), y = Inf, vjust = 1, hjust = 1, size = 6, family = 'serif')+
  theme(legend.title = element_blank(),
        axis.title.x = element_blank(),
        legend.position = c(0,1),
        legend.justification = c(0,1),
        legend.background = element_rect(fill = 'transparent', color = NA));#TB_q2_spp_plot

TB_q1_spp_plot = TB_q1_spp_df %>%
  ggplot()+
  geom_line(aes(x = Date, y = scale_n, group = Common_name, color = Common_name), size = 1.2)+
  scale_color_viridis(discrete = TRUE)+
  scale_y_continuous(name = "Scaled Abundance", expand = c(0.01,0.01))+
  scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
               date_labels = "%Y", expand = c(0.01,0.01))+
  theme_tufte()+
  geom_rangeframe(data = TB_q1_spp_df, aes(x = Date, y = scale_n),
                  sides = 'bl', color = 'black', inherit.aes = FALSE)+
  annotate('text', label = expression(italic(""^q*"D = 1")), x = as.Date("2019-12-31"), y = Inf, vjust = 1, hjust = 1, size = 6, family = 'serif')+
  theme(legend.title = element_blank(),
        axis.title.x = element_blank(),
        legend.position = c(0,1),
        legend.justification = c(0,1),
        legend.background = element_rect(fill = 'transparent', color = NA));#TB_q1_spp_plot

TB_q0.5_spp_plot = TB_q0.5_spp_df %>%
  ggplot()+
  geom_line(aes(x = Date, y = scale_n, group = Common_name, color = Common_name), size = 1.2)+
  scale_color_viridis(discrete = TRUE)+
  scale_y_continuous(name = "Scaled Abundance", expand = c(0.01,0.01))+
  scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
               date_labels = "%Y", expand = c(0.01,0.01))+
  theme_tufte()+
  geom_rangeframe(data = TB_q0.5_spp_df, aes(x = Date, y = scale_n),
                  sides = 'bl', color = 'black', inherit.aes = FALSE)+
  annotate('text', label = expression(italic(""^q*"D = 0.5")), x = as.Date("2019-12-31"), y = Inf, vjust = 1, hjust = 1, size = 6, family = 'serif')+
  theme(legend.title = element_blank(),
        axis.title.x = element_blank(),
        legend.position = c(0,1),
        legend.justification = c(0,1),
        legend.background = element_rect(fill = 'transparent', color = NA));#TB_q0.5_spp_plot

TB_q0.1_spp_plot = TB_q0.1_spp_df %>%
  ggplot()+
  geom_line(aes(x = Date, y = scale_n, group = Common_name, color = Common_name))+
  scale_color_viridis(discrete = TRUE)+
  scale_y_continuous(name = "Scaled Abundance", expand = c(0.01,0.01))+
  scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
               date_labels = "%Y", expand = c(0.01,0.01))+
  theme_tufte()+
  geom_rangeframe(data = TB_q0.1_spp_df, aes(x = Date, y = scale_n),
                  sides = 'bl', color = 'black', inherit.aes = FALSE)+
  annotate('text', label = expression(italic(""^q*"D = 0.1")), x = as.Date("2019-12-31"), y = Inf, vjust = 1, hjust = 1, size = 6, family = 'serif')+
  theme(legend.title = element_blank(),
        axis.title.x = element_blank(),
        legend.position = c(0,1),
        legend.justification = c(0,1),
        legend.background = element_rect(fill = 'transparent', color = NA));#TB_q0.1_spp_plot

grid.draw(rbind(ggplotGrob(TB_q0.5_spp_plot), ggplotGrob(TB_q2_spp_plot), size = 'last'))

@@

```{r trawl contributions,echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Figure 6. The contribution of individual trawl-dates to dissimilarity of the entire timeseries for diversity order q = 0.5 (top), q = 1 (middle), and q = 2 (bottom)." }

@@

@@

# plot contributions of each trawl to differences
TB_trawl_q0_dis2 %>%
  dplyr::filter(dis_type == "UqN")%>%
  ggplot(aes(x = Date, y = value))+
  geom_point()+
  geom_path()+
  scale_y_continuous(expand = c(0.0001,0.0001))+
   scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
               date_labels = "%Y")+
  theme_tufte()+
  geom_rangeframe(sides = "lb", color = "black")+
  annotate('text', label = expression(italic(''^q*"D = 0")), x = as.Date("2009-01-01"), y = Inf, size = 6, family = 'serif')+
  theme(axis.title = element_blank(),
        axis.text.x = element_blank())-> TB_q0_dis2_plot

TB_trawl_q0.1_dis2 %>%
  dplyr::filter(dis_type == "UqN")%>%
  ggplot(aes(x = Date, y = value))+
  geom_point()+
  geom_path()+
  scale_y_continuous(expand = c(0.0001,0.0001))+
   scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
               date_labels = "%Y")+
  theme_tufte()+
  geom_rangeframe(sides = "lb", color = "black")+
  annotate('text', label = expression(italic(''^q*"D = 0.1")), x = as.Date("2009-01-01"), y = Inf, size = 6, family = 'serif')+
  theme(axis.title = element_blank(),
        axis.text.x = element_blank())-> TB_q0.1_dis2_plot

TB_trawl_q0.5_dis2 %>%
  dplyr::filter(dis_type == "UqN")%>%
  ggplot(aes(x = Date, y = value))+
  geom_point()+
  geom_path()+
  scale_y_continuous(expand = c(0.0001,0.0001))+
   scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
               date_labels = "%Y")+
  theme_tufte()+
  geom_rangeframe(sides = "lb", color = "black")+
  annotate('text', label = expression(italic(''^q*"D = 0.5")), x = as.Date("2019-12-31"), y = Inf, size = 6, family = 'serif', vjust = 1, hjust =1)+
  theme(axis.title = element_blank(),
        axis.text.x = element_blank())-> TB_q0.5_dis2_plot

TB_trawl_q1_dis2 %>%
  dplyr::filter(dis_type == "UqN")%>%
  ggplot(aes(x = Date, y = value))+
  geom_point()+
  geom_path()+
  scale_y_continuous(expand = c(0.0001,0.0001))+
   scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
               date_labels = "%Y")+
  theme_tufte()+
  geom_rangeframe(sides = "lb", color = "black")+
  annotate('text', label = expression(italic(''^q*"D = 1")), x = as.Date("2019-12-31"), y = Inf, size = 6, family = 'serif', vjust = 1, hjust = 1)+
  theme(axis.title = element_blank(),
        axis.text.x = element_blank())-> TB_q1_dis2_plot
